Meta analysis of differential expression results from AMP-AD (Control vs AD, reprocessed RNASeq)

### 2017-05-16 code/Rmd/MetaAnalysis.Rmd
Temp Commit

---
title: "Meta analysis of differential expression results from AMP-AD (Control vs AD, reprocessed RNASeq)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knit2synapse)
synapseLogin()

knit2synapse::knitToFolderEntity(file = "./MetaAnalysis.Rmd", 
                                 parentId ="syn5569102",
                                 entityName = 'MetaAnalysis of Control vs AD from all three brain banks (Reprocessed RNASeq)')
```

@@

### Get curated gene list
```{r curate.genelist}
# Download enrichr gene sets from synapse
GL_OBJ = synGet('syn4867851')
ALL_USED_IDs = c(ALL_USED_IDs, GL_OBJ$properties$id)
load(GL_OBJ@filePath)

gsets = c("GO_Biological_Process", "Reactome_2015", "WikiPathways_2015")
GeneSets.Enrichr = GeneSets[gsets]

# Download AD related gene sets from synapse
GL_OBJ = synGet('syn4893059');
ALL_USED_IDs = c(ALL_USED_IDs, GL_OBJ$properties$id)
load(GL_OBJ@filePath)

>>>>

---
title: "Meta analysis of differential expression results from AMP-AD (Control vs AD, reprocessed RNASeq)"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knit2synapse)

knit2synapse::knitToFolderEntity(file = "./MetaAnalysis.Rmd", 
                                 parentId ="syn9622393",
                                 entityName = 'MetaAnalysis of Control vs AD (Reprocessed RNASeq)')
```

@@

### Get curated gene list
```{r curate.genelist}
# Download enrichr gene sets from synapse
GL_OBJ = synGet('syn4867851')
all.used.ids = 'syn4867851'
load(GL_OBJ@filePath)

gsets = c("GO_Biological_Process_2015", "Reactome_2016", "WikiPathways_2016")
GeneSets.Enrichr = GeneSets[gsets]

# Download AD genetic loci from synapse
AD = list(GeneticLoci = synGet('syn4891675')@filePath %>%
            read.table(header = F) %>% 
            unlist() %>%
            as.character())

list()
GL_OBJ = synGet('syn4893059');
ALL_USED_IDs = c(ALL_USED_IDs, GL_OBJ$properties$id)
load(GL_OBJ@filePath)
